Dataset-level report

### 2020-01-20 analysis/reports/dat_report_template.Rmd
set up to add portal manips

  manip_skew_plot

@@

  manip_simpson_plot

@@

>>>>

  print(manip_skew_plot)

@@

  print(manip_simpson_plot)

@@

if(this_dataset == "portal_plants_manip") {
  all_di_manip <- readd(all_di_manip, cache = cache)

  manip_skew_plot <- ggplot(data = all_di_manip, aes(x = treatment, y = skew_percentile)) +
    geom_point() +
    facet_wrap(vars(season, singletons)) +
    theme_bw()

  print(manip_skew_plot)

  manip_simpson_plot <- ggplot(data = all_di_manip, aes(x = treatment, y = simpson_percentile)) +
    geom_point() +
    facet_wrap(vars(season, singletons)) +
    theme_bw()

  print(manip_simpson_plot)
}
```
